\tool{}: Specification- and Syntax-based Automated Testing Linguistic Capabilities of NLP Models

### 2023-03-16 paper/fse23/tables/test-results-hs-all-numbers.tex
icse24

\DefMacro{test-results-hs-lc2-num-exps}{3,124}
\DefMacro{test-results-hs-model0-lc2-num-all-fail}{3,220}
\DefMacro{test-results-hs-model0-lc2-num-seed-failrate}{98.57}
\DefMacro{test-results-hs-model0-lc2-num-exp-failrate}{98.66}
\DefMacro{test-results-hs-model0-lc2-num-all-failrate}{98.65}
\DefMacro{test-results-hs-model0-lc2-num-pass-to-fail}{18}

@@

\DefMacro{test-results-hs-lc18-num-exps}{300,704}
\DefMacro{test-results-hs-model0-lc18-num-all-fail}{48,804}
\DefMacro{test-results-hs-model0-lc18-num-seed-failrate}{13.78}
\DefMacro{test-results-hs-model0-lc18-num-exp-failrate}{14.14}
\DefMacro{test-results-hs-model0-lc18-num-all-failrate}{14.09}
\DefMacro{test-results-hs-model0-lc18-num-pass-to-fail}{4,831}

@@

\DefMacro{test-results-hs-lc1-num-exps}{2,959}
\DefMacro{test-results-hs-model0-lc1-num-all-fail}{3,067}
\DefMacro{test-results-hs-model0-lc1-num-seed-failrate}{98.57}
\DefMacro{test-results-hs-model0-lc1-num-exp-failrate}{98.99}
\DefMacro{test-results-hs-model0-lc1-num-all-failrate}{98.97}
\DefMacro{test-results-hs-model0-lc1-num-pass-to-fail}{23}

@@

\DefMacro{test-results-hs-lc4-num-exps}{2,689}
\DefMacro{test-results-hs-model0-lc4-num-all-fail}{2,770}
\DefMacro{test-results-hs-model0-lc4-num-seed-failrate}{97.74}
\DefMacro{test-results-hs-model0-lc4-num-exp-failrate}{98.18}
\DefMacro{test-results-hs-model0-lc4-num-all-failrate}{98.16}
\DefMacro{test-results-hs-model0-lc4-num-pass-to-fail}{9}

@@

\DefMacro{test-results-hs-model0-lc0-num-all-fail}{920}
\DefMacro{test-results-hs-model0-lc0-num-seed-failrate}{97.14}
\DefMacro{test-results-hs-model0-lc0-num-exp-failrate}{98.12}
\DefMacro{test-results-hs-model0-lc0-num-all-failrate}{97.98}
\DefMacro{test-results-hs-model0-lc0-num-pass-to-fail}{22}

@@

\DefMacro{test-results-hs-lc10-num-seeds}{11,968}
\DefMacro{test-results-hs-lc10-num-exps}{44,890}
\DefMacro{test-results-hs-model0-lc10-num-all-fail}{49,929}
\DefMacro{test-results-hs-model0-lc10-num-seed-failrate}{60.60}
\DefMacro{test-results-hs-model0-lc10-num-exp-failrate}{95.07}
\DefMacro{test-results-hs-model0-lc10-num-all-failrate}{87.81}
\DefMacro{test-results-hs-model0-lc10-num-pass-to-fail}{1,169}

@@

\DefMacro{test-results-hs-lc11-num-exps}{42,840}
\DefMacro{test-results-hs-model0-lc11-num-all-fail}{47,294}
\DefMacro{test-results-hs-model0-lc11-num-seed-failrate}{58.92}
\DefMacro{test-results-hs-model0-lc11-num-exp-failrate}{93.94}
\DefMacro{test-results-hs-model0-lc11-num-all-failrate}{86.29}
\DefMacro{test-results-hs-model0-lc11-num-pass-to-fail}{1,726}

@@

\DefMacro{test-results-hs-lc12-num-exps}{126,742}
\DefMacro{test-results-hs-model0-lc12-num-all-fail}{145,761}
\DefMacro{test-results-hs-model0-lc12-num-seed-failrate}{97.03}
\DefMacro{test-results-hs-model0-lc12-num-exp-failrate}{97.11}
\DefMacro{test-results-hs-model0-lc12-num-all-failrate}{97.10}
\DefMacro{test-results-hs-model0-lc12-num-pass-to-fail}{2,290}

@@

\DefMacro{test-results-hs-lc8-num-exps}{49,743}
\DefMacro{test-results-hs-model0-lc8-num-all-fail}{50,158}
\DefMacro{test-results-hs-model0-lc8-num-seed-failrate}{97.34}
\DefMacro{test-results-hs-model0-lc8-num-exp-failrate}{97.23}
\DefMacro{test-results-hs-model0-lc8-num-all-failrate}{97.23}
\DefMacro{test-results-hs-model0-lc8-num-pass-to-fail}{164}

@@

\DefMacro{test-results-hs-lc6-num-exps}{17,318}
\DefMacro{test-results-hs-model0-lc6-num-all-fail}{17,597}
\DefMacro{test-results-hs-model0-lc6-num-seed-failrate}{97.14}
\DefMacro{test-results-hs-model0-lc6-num-exp-failrate}{97.10}
\DefMacro{test-results-hs-model0-lc6-num-all-failrate}{97.10}
\DefMacro{test-results-hs-model0-lc6-num-pass-to-fail}{70}

@@

\DefMacro{test-results-hs-lc15-num-exps}{160,927}
\DefMacro{test-results-hs-model0-lc15-num-all-fail}{178,058}
\DefMacro{test-results-hs-model0-lc15-num-seed-failrate}{97.25}
\DefMacro{test-results-hs-model0-lc15-num-exp-failrate}{96.86}
\DefMacro{test-results-hs-model0-lc15-num-all-failrate}{96.91}
\DefMacro{test-results-hs-model0-lc15-num-pass-to-fail}{3,078}

@@

\DefMacro{test-results-hs-lc14-num-exps}{185,267}
\DefMacro{test-results-hs-model0-lc14-num-all-fail}{202,023}
\DefMacro{test-results-hs-model0-lc14-num-seed-failrate}{97.37}
\DefMacro{test-results-hs-model0-lc14-num-exp-failrate}{97.06}
\DefMacro{test-results-hs-model0-lc14-num-all-failrate}{97.09}
\DefMacro{test-results-hs-model0-lc14-num-pass-to-fail}{2,956}

@@

\DefMacro{test-results-hs-lc3-num-exps}{5,664}
\DefMacro{test-results-hs-model0-lc3-num-all-fail}{5,730}
\DefMacro{test-results-hs-model0-lc3-num-seed-failrate}{97.86}
\DefMacro{test-results-hs-model0-lc3-num-exp-failrate}{98.75}
\DefMacro{test-results-hs-model0-lc3-num-all-failrate}{98.73}
\DefMacro{test-results-hs-model0-lc3-num-pass-to-fail}{30}

@@

\DefMacro{test-results-hs-model0-lc16-num-all-fail}{1}
\DefMacro{test-results-hs-model0-lc16-num-seed-failrate}{20.00}
\DefMacro{test-results-hs-model0-lc16-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc16-num-all-failrate}{7.14}

@@

@@

\DefMacro{test-results-hs-lc9-num-exps}{15,761}
\DefMacro{test-results-hs-model0-lc9-num-all-fail}{11,939}
\DefMacro{test-results-hs-model0-lc9-num-seed-failrate}{71.04}
\DefMacro{test-results-hs-model0-lc9-num-exp-failrate}{72.59}
\DefMacro{test-results-hs-model0-lc9-num-all-failrate}{72.52}
\DefMacro{test-results-hs-model0-lc9-num-pass-to-fail}{75}

@@

\DefMacro{test-results-hs-lc13-num-exps}{243,739}
\DefMacro{test-results-hs-model0-lc13-num-all-fail}{77,191}
\DefMacro{test-results-hs-model0-lc13-num-seed-failrate}{26.90}
\DefMacro{test-results-hs-model0-lc13-num-exp-failrate}{27.89}
\DefMacro{test-results-hs-model0-lc13-num-all-failrate}{27.77}
\DefMacro{test-results-hs-model0-lc13-num-pass-to-fail}{5,222}

@@

\DefMacro{test-results-hs-lc7-num-exps}{7,881}
\DefMacro{test-results-hs-model0-lc7-num-all-fail}{2,739}
\DefMacro{test-results-hs-model0-lc7-num-seed-failrate}{30.89}
\DefMacro{test-results-hs-model0-lc7-num-exp-failrate}{33.21}
\DefMacro{test-results-hs-model0-lc7-num-all-failrate}{33.10}
\DefMacro{test-results-hs-model0-lc7-num-pass-to-fail}{44}

@@

\DefMacro{test-results-hs-model0-lc17-num-all-fail}{14}
\DefMacro{test-results-hs-model0-lc17-num-seed-failrate}{4.88}
\DefMacro{test-results-hs-model0-lc17-num-exp-failrate}{6.59}
\DefMacro{test-results-hs-model0-lc17-num-all-failrate}{6.28}
\DefMacro{test-results-hs-model0-lc17-num-pass-to-fail}{1}

@@

\DefMacro{test-results-hs-lc5-num-exps}{4,163}
\DefMacro{test-results-hs-model0-lc5-num-all-fail}{4,261}
\DefMacro{test-results-hs-model0-lc5-num-seed-failrate}{99.29}
\DefMacro{test-results-hs-model0-lc5-num-exp-failrate}{99.02}
\DefMacro{test-results-hs-model0-lc5-num-all-failrate}{99.02}
\DefMacro{test-results-hs-model0-lc5-num-pass-to-fail}{1}
\DefMacro{test-results-hs-model1-lc2-num-all-fail}{87}
\DefMacro{test-results-hs-model1-lc2-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc2-num-exp-failrate}{2.78}
\DefMacro{test-results-hs-model1-lc2-num-all-failrate}{2.67}
\DefMacro{test-results-hs-model1-lc2-num-pass-to-fail}{31}
\DefMacro{test-results-hs-model1-lc18-num-all-fail}{346,320}
\DefMacro{test-results-hs-model1-lc18-num-seed-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc18-num-exp-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc18-num-all-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc18-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc1-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc1-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc1-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc1-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc1-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc4-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc4-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc4-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc4-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc4-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc0-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc0-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc0-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc0-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc0-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc10-num-all-fail}{5,984}
\DefMacro{test-results-hs-model1-lc10-num-seed-failrate}{50.00}
\DefMacro{test-results-hs-model1-lc10-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc10-num-all-failrate}{10.52}
\DefMacro{test-results-hs-model1-lc10-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc11-num-all-fail}{5,984}
\DefMacro{test-results-hs-model1-lc11-num-seed-failrate}{50.00}
\DefMacro{test-results-hs-model1-lc11-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc11-num-all-failrate}{10.92}
\DefMacro{test-results-hs-model1-lc11-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc12-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc12-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc12-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc12-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc12-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc8-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc8-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc8-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc8-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc8-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc6-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc6-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc6-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc6-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc6-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc15-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc15-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc15-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc15-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc15-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc14-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc14-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc14-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc14-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc14-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc3-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc3-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc3-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc3-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc3-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc16-num-all-fail}{14}
\DefMacro{test-results-hs-model1-lc16-num-seed-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc16-num-exp-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc16-num-all-failrate}{100.00}

>>>>

\DefMacro{test-results-hs-lc2-num-exps}{1,791}
\DefMacro{test-results-hs-bl-lc2-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc2-num-all-fail}{1,419}
\DefMacro{test-results-hs-model0-lc2-num-seed-failrate}{72.14}
\DefMacro{test-results-hs-model0-lc2-num-exp-failrate}{73.59}
\DefMacro{test-results-hs-model0-lc2-num-all-failrate}{73.49}
\DefMacro{test-results-hs-model0-lc2-num-pass-to-fail}{48}
\DefMacro{test-results-hs-bl-model0-lc2-num-fail}{101}
\DefMacro{test-results-hs-bl-model0-lc2-num-failrate}{72.14}
\DefMacro{test-results-hs-lc19}{Denouncements of hate that make direct reference to it}
\DefMacro{test-results-hs-lc19-num-seeds}{34,212}
\DefMacro{test-results-hs-lc19-num-exps}{209,389}
\DefMacro{test-results-hs-bl-lc19-num-tcs}{141}
\DefMacro{test-results-hs-model0-lc19-num-all-fail}{33,397}
\DefMacro{test-results-hs-model0-lc19-num-seed-failrate}{13.06}
\DefMacro{test-results-hs-model0-lc19-num-exp-failrate}{13.82}
\DefMacro{test-results-hs-model0-lc19-num-all-failrate}{13.71}
\DefMacro{test-results-hs-model0-lc19-num-pass-to-fail}{1,888}
\DefMacro{test-results-hs-bl-model0-lc19-num-fail}{4}
\DefMacro{test-results-hs-bl-model0-lc19-num-failrate}{2.84}

@@

\DefMacro{test-results-hs-lc18-num-exps}{258,317}
\DefMacro{test-results-hs-bl-lc18-num-tcs}{173}
\DefMacro{test-results-hs-model0-lc18-num-all-fail}{38,262}
\DefMacro{test-results-hs-model0-lc18-num-seed-failrate}{11.96}
\DefMacro{test-results-hs-model0-lc18-num-exp-failrate}{12.70}
\DefMacro{test-results-hs-model0-lc18-num-all-failrate}{12.59}
\DefMacro{test-results-hs-model0-lc18-num-pass-to-fail}{2,049}
\DefMacro{test-results-hs-bl-model0-lc18-num-fail}{17}
\DefMacro{test-results-hs-bl-model0-lc18-num-failrate}{9.83}

@@

\DefMacro{test-results-hs-lc1-num-exps}{2,433}
\DefMacro{test-results-hs-bl-lc1-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc1-num-all-fail}{1,935}
\DefMacro{test-results-hs-model0-lc1-num-seed-failrate}{73.57}
\DefMacro{test-results-hs-model0-lc1-num-exp-failrate}{75.30}
\DefMacro{test-results-hs-model0-lc1-num-all-failrate}{75.20}
\DefMacro{test-results-hs-model0-lc1-num-pass-to-fail}{86}
\DefMacro{test-results-hs-bl-model0-lc1-num-fail}{103}
\DefMacro{test-results-hs-bl-model0-lc1-num-failrate}{73.57}

@@

\DefMacro{test-results-hs-lc4-num-exps}{698}
\DefMacro{test-results-hs-bl-lc4-num-tcs}{133}
\DefMacro{test-results-hs-model0-lc4-num-all-fail}{654}
\DefMacro{test-results-hs-model0-lc4-num-seed-failrate}{78.95}
\DefMacro{test-results-hs-model0-lc4-num-exp-failrate}{78.65}
\DefMacro{test-results-hs-model0-lc4-num-all-failrate}{78.70}
\DefMacro{test-results-hs-model0-lc4-num-pass-to-fail}{14}
\DefMacro{test-results-hs-bl-model0-lc4-num-fail}{104}
\DefMacro{test-results-hs-bl-model0-lc4-num-failrate}{78.20}

@@

\DefMacro{test-results-hs-bl-lc0-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc0-num-all-fail}{772}
\DefMacro{test-results-hs-model0-lc0-num-seed-failrate}{77.14}
\DefMacro{test-results-hs-model0-lc0-num-exp-failrate}{83.10}
\DefMacro{test-results-hs-model0-lc0-num-all-failrate}{82.22}
\DefMacro{test-results-hs-model0-lc0-num-pass-to-fail}{27}
\DefMacro{test-results-hs-bl-model0-lc0-num-fail}{108}
\DefMacro{test-results-hs-bl-model0-lc0-num-failrate}{77.14}

@@

\DefMacro{test-results-hs-lc10-num-seeds}{13,442}
\DefMacro{test-results-hs-lc10-num-exps}{41,806}
\DefMacro{test-results-hs-bl-lc10-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc10-num-all-fail}{36,054}
\DefMacro{test-results-hs-model0-lc10-num-seed-failrate}{42.47}
\DefMacro{test-results-hs-model0-lc10-num-exp-failrate}{72.59}
\DefMacro{test-results-hs-model0-lc10-num-all-failrate}{65.26}
\DefMacro{test-results-hs-model0-lc10-num-pass-to-fail}{751}
\DefMacro{test-results-hs-bl-model0-lc10-num-fail}{108}
\DefMacro{test-results-hs-bl-model0-lc10-num-failrate}{77.14}

@@

\DefMacro{test-results-hs-lc11-num-exps}{40,942}
\DefMacro{test-results-hs-bl-lc11-num-tcs}{133}
\DefMacro{test-results-hs-model0-lc11-num-all-fail}{34,859}
\DefMacro{test-results-hs-model0-lc11-num-seed-failrate}{45.96}
\DefMacro{test-results-hs-model0-lc11-num-exp-failrate}{71.71}
\DefMacro{test-results-hs-model0-lc11-num-all-failrate}{65.88}
\DefMacro{test-results-hs-model0-lc11-num-pass-to-fail}{764}
\DefMacro{test-results-hs-bl-model0-lc11-num-fail}{101}
\DefMacro{test-results-hs-bl-model0-lc11-num-failrate}{75.94}

@@

\DefMacro{test-results-hs-lc12-num-exps}{105,280}
\DefMacro{test-results-hs-bl-lc12-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc12-num-all-fail}{114,827}
\DefMacro{test-results-hs-model0-lc12-num-seed-failrate}{89.68}
\DefMacro{test-results-hs-model0-lc12-num-exp-failrate}{89.15}
\DefMacro{test-results-hs-model0-lc12-num-all-failrate}{89.25}
\DefMacro{test-results-hs-model0-lc12-num-pass-to-fail}{954}
\DefMacro{test-results-hs-bl-model0-lc12-num-fail}{109}
\DefMacro{test-results-hs-bl-model0-lc12-num-failrate}{77.86}

@@

\DefMacro{test-results-hs-lc8-num-exps}{10,755}
\DefMacro{test-results-hs-bl-lc8-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc8-num-all-fail}{9,874}
\DefMacro{test-results-hs-model0-lc8-num-seed-failrate}{78.66}
\DefMacro{test-results-hs-model0-lc8-num-exp-failrate}{78.34}
\DefMacro{test-results-hs-model0-lc8-num-all-failrate}{78.38}
\DefMacro{test-results-hs-model0-lc8-num-pass-to-fail}{114}
\DefMacro{test-results-hs-bl-model0-lc8-num-fail}{98}
\DefMacro{test-results-hs-bl-model0-lc8-num-failrate}{70.00}

@@

\DefMacro{test-results-hs-lc6-num-exps}{3,923}
\DefMacro{test-results-hs-bl-lc6-num-tcs}{144}
\DefMacro{test-results-hs-model0-lc6-num-all-fail}{1,214}
\DefMacro{test-results-hs-model0-lc6-num-seed-failrate}{23.60}
\DefMacro{test-results-hs-model0-lc6-num-exp-failrate}{26.10}
\DefMacro{test-results-hs-model0-lc6-num-all-failrate}{25.68}
\DefMacro{test-results-hs-model0-lc6-num-pass-to-fail}{84}
\DefMacro{test-results-hs-bl-model0-lc6-num-fail}{108}
\DefMacro{test-results-hs-bl-model0-lc6-num-failrate}{75.00}

@@

\DefMacro{test-results-hs-lc15-num-exps}{141,890}
\DefMacro{test-results-hs-bl-lc15-num-tcs}{133}
\DefMacro{test-results-hs-model0-lc15-num-all-fail}{135,520}
\DefMacro{test-results-hs-model0-lc15-num-seed-failrate}{82.88}
\DefMacro{test-results-hs-model0-lc15-num-exp-failrate}{82.19}
\DefMacro{test-results-hs-model0-lc15-num-all-failrate}{82.28}
\DefMacro{test-results-hs-model0-lc15-num-pass-to-fail}{1,713}
\DefMacro{test-results-hs-bl-model0-lc15-num-fail}{100}
\DefMacro{test-results-hs-bl-model0-lc15-num-failrate}{75.19}

@@

\DefMacro{test-results-hs-lc14-num-exps}{127,800}
\DefMacro{test-results-hs-bl-lc14-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc14-num-all-fail}{127,991}
\DefMacro{test-results-hs-model0-lc14-num-seed-failrate}{85.52}
\DefMacro{test-results-hs-model0-lc14-num-exp-failrate}{84.89}
\DefMacro{test-results-hs-model0-lc14-num-all-failrate}{84.98}
\DefMacro{test-results-hs-model0-lc14-num-pass-to-fail}{1,357}
\DefMacro{test-results-hs-bl-model0-lc14-num-fail}{107}
\DefMacro{test-results-hs-bl-model0-lc14-num-failrate}{76.43}

@@

\DefMacro{test-results-hs-lc3-num-exps}{2,674}
\DefMacro{test-results-hs-bl-lc3-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc3-num-all-fail}{2,385}
\DefMacro{test-results-hs-model0-lc3-num-seed-failrate}{83.57}
\DefMacro{test-results-hs-model0-lc3-num-exp-failrate}{84.82}
\DefMacro{test-results-hs-model0-lc3-num-all-failrate}{84.75}
\DefMacro{test-results-hs-model0-lc3-num-pass-to-fail}{44}
\DefMacro{test-results-hs-bl-model0-lc3-num-fail}{115}
\DefMacro{test-results-hs-bl-model0-lc3-num-failrate}{82.14}

@@

\DefMacro{test-results-hs-bl-lc16-num-tcs}{126}
\DefMacro{test-results-hs-model0-lc16-num-all-fail}{12}
\DefMacro{test-results-hs-model0-lc16-num-seed-failrate}{60.00}
\DefMacro{test-results-hs-model0-lc16-num-exp-failrate}{100.00}
\DefMacro{test-results-hs-model0-lc16-num-all-failrate}{85.71}

@@

\DefMacro{test-results-hs-bl-model0-lc16-num-fail}{9}
\DefMacro{test-results-hs-bl-model0-lc16-num-failrate}{7.14}

@@

\DefMacro{test-results-hs-lc9-num-exps}{3,360}
\DefMacro{test-results-hs-bl-lc9-num-tcs}{100}
\DefMacro{test-results-hs-model0-lc9-num-all-fail}{548}
\DefMacro{test-results-hs-model0-lc9-num-seed-failrate}{11.41}
\DefMacro{test-results-hs-model0-lc9-num-exp-failrate}{13.93}
\DefMacro{test-results-hs-model0-lc9-num-all-failrate}{13.49}
\DefMacro{test-results-hs-model0-lc9-num-pass-to-fail}{20}
\DefMacro{test-results-hs-bl-model0-lc9-num-fail}{1}
\DefMacro{test-results-hs-bl-model0-lc9-num-failrate}{1.00}

@@

\DefMacro{test-results-hs-lc13-num-exps}{209,980}
\DefMacro{test-results-hs-bl-lc13-num-tcs}{133}
\DefMacro{test-results-hs-model0-lc13-num-all-fail}{42,530}
\DefMacro{test-results-hs-model0-lc13-num-seed-failrate}{16.82}
\DefMacro{test-results-hs-model0-lc13-num-exp-failrate}{17.51}
\DefMacro{test-results-hs-model0-lc13-num-all-failrate}{17.42}
\DefMacro{test-results-hs-model0-lc13-num-pass-to-fail}{2,184}
\DefMacro{test-results-hs-bl-model0-lc13-num-fail}{13}
\DefMacro{test-results-hs-bl-model0-lc13-num-failrate}{9.77}

@@

\DefMacro{test-results-hs-lc7-num-exps}{1,667}
\DefMacro{test-results-hs-bl-lc7-num-tcs}{111}
\DefMacro{test-results-hs-model0-lc7-num-all-fail}{1,263}
\DefMacro{test-results-hs-model0-lc7-num-seed-failrate}{63.29}
\DefMacro{test-results-hs-model0-lc7-num-exp-failrate}{60.77}
\DefMacro{test-results-hs-model0-lc7-num-all-failrate}{61.25}
\DefMacro{test-results-hs-model0-lc7-num-pass-to-fail}{10}
\DefMacro{test-results-hs-bl-model0-lc7-num-fail}{18}
\DefMacro{test-results-hs-bl-model0-lc7-num-failrate}{16.22}

@@

\DefMacro{test-results-hs-bl-lc17-num-tcs}{189}
\DefMacro{test-results-hs-model0-lc17-num-all-fail}{84}
\DefMacro{test-results-hs-model0-lc17-num-seed-failrate}{46.34}
\DefMacro{test-results-hs-model0-lc17-num-exp-failrate}{35.71}
\DefMacro{test-results-hs-model0-lc17-num-all-failrate}{37.67}
\DefMacro{test-results-hs-model0-lc17-num-pass-to-fail}{7}
\DefMacro{test-results-hs-bl-model0-lc17-num-fail}{23}
\DefMacro{test-results-hs-bl-model0-lc17-num-failrate}{12.17}

@@

\DefMacro{test-results-hs-lc5-num-exps}{992}
\DefMacro{test-results-hs-bl-lc5-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc5-num-all-fail}{804}
\DefMacro{test-results-hs-model0-lc5-num-seed-failrate}{70.71}
\DefMacro{test-results-hs-model0-lc5-num-exp-failrate}{71.07}
\DefMacro{test-results-hs-model0-lc5-num-all-failrate}{71.02}
\DefMacro{test-results-hs-model0-lc5-num-pass-to-fail}{13}
\DefMacro{test-results-hs-bl-model0-lc5-num-fail}{99}
\DefMacro{test-results-hs-bl-model0-lc5-num-failrate}{70.71}
\DefMacro{test-results-hs-model1-lc2-num-all-fail}{897}
\DefMacro{test-results-hs-model1-lc2-num-seed-failrate}{42.14}
\DefMacro{test-results-hs-model1-lc2-num-exp-failrate}{46.79}
\DefMacro{test-results-hs-model1-lc2-num-all-failrate}{46.45}
\DefMacro{test-results-hs-model1-lc2-num-pass-to-fail}{157}
\DefMacro{test-results-hs-bl-model1-lc2-num-fail}{59}
\DefMacro{test-results-hs-bl-model1-lc2-num-failrate}{42.14}
\DefMacro{test-results-hs-model1-lc19-num-all-fail}{146,576}
\DefMacro{test-results-hs-model1-lc19-num-seed-failrate}{60.74}
\DefMacro{test-results-hs-model1-lc19-num-exp-failrate}{60.08}
\DefMacro{test-results-hs-model1-lc19-num-all-failrate}{60.17}
\DefMacro{test-results-hs-model1-lc19-num-pass-to-fail}{3,362}
\DefMacro{test-results-hs-bl-model1-lc19-num-fail}{7}
\DefMacro{test-results-hs-bl-model1-lc19-num-failrate}{4.96}
\DefMacro{test-results-hs-model1-lc18-num-all-fail}{150,815}
\DefMacro{test-results-hs-model1-lc18-num-seed-failrate}{48.34}
\DefMacro{test-results-hs-model1-lc18-num-exp-failrate}{49.85}
\DefMacro{test-results-hs-model1-lc18-num-all-failrate}{49.62}
\DefMacro{test-results-hs-model1-lc18-num-pass-to-fail}{4,861}
\DefMacro{test-results-hs-bl-model1-lc18-num-fail}{5}
\DefMacro{test-results-hs-bl-model1-lc18-num-failrate}{2.89}
\DefMacro{test-results-hs-model1-lc1-num-all-fail}{1,230}
\DefMacro{test-results-hs-model1-lc1-num-seed-failrate}{46.43}
\DefMacro{test-results-hs-model1-lc1-num-exp-failrate}{47.88}
\DefMacro{test-results-hs-model1-lc1-num-all-failrate}{47.80}
\DefMacro{test-results-hs-model1-lc1-num-pass-to-fail}{410}
\DefMacro{test-results-hs-bl-model1-lc1-num-fail}{67}
\DefMacro{test-results-hs-bl-model1-lc1-num-failrate}{47.86}
\DefMacro{test-results-hs-model1-lc4-num-all-fail}{681}
\DefMacro{test-results-hs-model1-lc4-num-seed-failrate}{84.21}
\DefMacro{test-results-hs-model1-lc4-num-exp-failrate}{81.52}
\DefMacro{test-results-hs-model1-lc4-num-all-failrate}{81.95}
\DefMacro{test-results-hs-model1-lc4-num-pass-to-fail}{26}
\DefMacro{test-results-hs-bl-model1-lc4-num-fail}{110}
\DefMacro{test-results-hs-bl-model1-lc4-num-failrate}{82.71}
\DefMacro{test-results-hs-model1-lc0-num-all-fail}{753}
\DefMacro{test-results-hs-model1-lc0-num-seed-failrate}{77.86}
\DefMacro{test-results-hs-model1-lc0-num-exp-failrate}{80.60}
\DefMacro{test-results-hs-model1-lc0-num-all-failrate}{80.19}
\DefMacro{test-results-hs-model1-lc0-num-pass-to-fail}{29}
\DefMacro{test-results-hs-bl-model1-lc0-num-fail}{109}
\DefMacro{test-results-hs-bl-model1-lc0-num-failrate}{77.86}
\DefMacro{test-results-hs-model1-lc10-num-all-fail}{28,848}
\DefMacro{test-results-hs-model1-lc10-num-seed-failrate}{50.23}
\DefMacro{test-results-hs-model1-lc10-num-exp-failrate}{52.85}
\DefMacro{test-results-hs-model1-lc10-num-all-failrate}{52.22}
\DefMacro{test-results-hs-model1-lc10-num-pass-to-fail}{762}
\DefMacro{test-results-hs-bl-model1-lc10-num-fail}{93}
\DefMacro{test-results-hs-bl-model1-lc10-num-failrate}{66.43}
\DefMacro{test-results-hs-model1-lc11-num-all-fail}{28,308}
\DefMacro{test-results-hs-model1-lc11-num-seed-failrate}{49.72}
\DefMacro{test-results-hs-model1-lc11-num-exp-failrate}{54.61}
\DefMacro{test-results-hs-model1-lc11-num-all-failrate}{53.50}
\DefMacro{test-results-hs-model1-lc11-num-pass-to-fail}{745}
\DefMacro{test-results-hs-bl-model1-lc11-num-fail}{69}
\DefMacro{test-results-hs-bl-model1-lc11-num-failrate}{51.88}
\DefMacro{test-results-hs-model1-lc12-num-all-fail}{90,337}
\DefMacro{test-results-hs-model1-lc12-num-seed-failrate}{66.01}
\DefMacro{test-results-hs-model1-lc12-num-exp-failrate}{71.15}
\DefMacro{test-results-hs-model1-lc12-num-all-failrate}{70.21}
\DefMacro{test-results-hs-model1-lc12-num-pass-to-fail}{1,913}
\DefMacro{test-results-hs-bl-model1-lc12-num-fail}{116}
\DefMacro{test-results-hs-bl-model1-lc12-num-failrate}{82.86}
\DefMacro{test-results-hs-model1-lc8-num-all-fail}{2,702}
\DefMacro{test-results-hs-model1-lc8-num-seed-failrate}{18.46}
\DefMacro{test-results-hs-model1-lc8-num-exp-failrate}{21.96}
\DefMacro{test-results-hs-model1-lc8-num-all-failrate}{21.45}
\DefMacro{test-results-hs-model1-lc8-num-pass-to-fail}{151}
\DefMacro{test-results-hs-bl-model1-lc8-num-fail}{93}
\DefMacro{test-results-hs-bl-model1-lc8-num-failrate}{66.43}
\DefMacro{test-results-hs-model1-lc6-num-all-fail}{395}
\DefMacro{test-results-hs-model1-lc6-num-seed-failrate}{5.71}
\DefMacro{test-results-hs-model1-lc6-num-exp-failrate}{8.90}
\DefMacro{test-results-hs-model1-lc6-num-all-failrate}{8.35}
\DefMacro{test-results-hs-model1-lc6-num-pass-to-fail}{90}
\DefMacro{test-results-hs-bl-model1-lc6-num-fail}{56}
